---
title: "Sustainability in Fashion"
author: "Reese Putnam"
date: "2025-01-24"
output: html_document
---

In this project we will find the countrys with the best sustanbile fashion brands and if they have recycling prgram efforts to sustain their production. 


```{r}
install.packages("tidyverse")
install.packages("ggplot2")
install.packages("dplyr")
install.packages("tidyr")
```

```{r}
library(tidyverse)
library(ggplot2)
library(dplyr)
library(tidyr)
```

```{r}
data <- read_csv("sustainable_fashion_trends.csv")
```
The data we are using is the sustainable fashion trends data set found for free on Kaggle. This data set has 5000 rows and 15 columns showing various insights on brands and their usuage of resources to create their clothing. We will use this data set to see which cpuntry's have the most sustainable brands and what resources they use to creat their clothing that contributes to their sustainability.

```{r}
str(data)
summary(data)
```
Now that we have seen the structre of our data set we first need to check if there is any missing values in the data set and remove if needed.

```{r}
colSums(is.na(data))
```

As shown above we see there is no data missing in each column so we can begin analzing and visualizing the data.

```{r}
ggplot(data, aes(x= Sustainability_Rating)) +
  geom_bar(fill= "blue") +
  ggtitle( "Sustainability Rating")
```
We can see a pretty even rating excpet for a majority being rated B in sustainability

```{r}
country_ratings <- data %>%
  group_by( Country, Sustainability_Rating) %>%
  summarise(Count = n())

ggplot(country_ratings, aes(x= Country,y= Count, fill= Sustainability_Rating))+
  geom_bar(stat="identity", position = "dodge")+
  ggtitle("Sustainability Rating by Country") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
From the graph above we can observe that France, India, and Italy have the highest A sustainability rating compared to the other countrys. 

```{r}
ggplot(data, aes(x= Country, fill= Material_Type))+
  geom_bar(stat="Count", position= "dodge") +
  ggtitle("Country's Most Popular Material") +
  xlab("Country")+
  ylab("Count") +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
There shows to be a consistent use of all material expect for Australia having the most use of recycled polyester and Italy using Hemp. 

```{r}
carbon_footprint <- data %>%
  group_by( Country, Carbon_Footprint_MT) %>%
  summarise(count= n())

ggplot(carbon_footprint, aes(x= Country, y= count, fill= Carbon_Footprint_MT))+
  geom_bar(stat="identity")+
  ggtitle("Carbon Footprint by Country")+
  xlab("Country")+
  ylab("Count")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
From the chart above it shows a correlation between all country's having a similar carbon footprint except for Japan showing to have a noticablly smaller cabon footprint than the rest of the countrys. 

```{r}
water_usage <- data %>%
  group_by(Country, Water_Usage_Liters) %>%
  summarise(count= n())
  
ggplot(water_usage, aes(x= Country, y= count, fill= Water_Usage_Liters)) +
  geom_bar(stat= "identity", postion= "dodge")+
  ggtitle("Water Usage by Country")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Similar to the carbon footprint graph above Japan seemingly has a lower water usuage in their production. 

```{r}
waste_production <- data %>%
  group_by(Country, Waste_Production_KG) %>%
  summarise(count = n())

ggplot(waste_production, aes(x=Country, y= Waste_Production_KG, fill= Waste_Production_KG))+
  geom_bar(stat= "identity", postion= "dodge")+
  ggtitle("Waste Prodction by Country")+
  xlab("Country")+
  ylab("Waste Production")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
We can start to see a trend in Japan having a lower amount of emmissions when creating clothing but France is showing in this particular graph to have a significally less waste production compared to the rest of the countries. 

Now that we have compared the carbon footprint, water usuage, and waste prodution as factors that contribute to each country's sustainability let's see if price will show any contribution to that score as well.

```{r}
ggplot(data, aes(x= Sustainability_Rating, y= Average_Price_USD, fill= Sustainability_Rating))+
  geom_boxplot()+
  ggtitle("Avergae Price by Sustainability Rating")+
  xlab("Sustainability Rating")+
  ylab("Average Price (USD)")
```
There isn't any trend shown in the graph above assuming that price effects the sustainability of the country. So we will see if the certifications show any trend in sustainability
```{r}
ggplot(data, aes(x= Country, fill= Certifications))+
  geom_bar(stat= "Count", position= "dodge")+
  ggtitle("Certifications by Country")+
  xlab("Country")+
  ylab("Count")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```
Finally we will see which country's have recycling programs in place.

```{r}
ggplot(data, aes(x= Country, fill= Recycling_Programs))+
  geom_bar(stat="Count", position= "dodge")+
  ggtitle("Recycling Programs by Country")+
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

